Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi

### 2011-12-02 ms.tex
Added in the VERITAS author list

%\title{VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
%\title{Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
\title{Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi}
\author{N. Karlsson\altaffilmark{1,2}, M. Pohl\altaffilmark{3,4}}
\affil{(the VERITAS collaboration)} 
%%\email{nkarlsson@physics.umn.edu}
\and
\author{S. Federici\altaffilmark{3,4}, C. Pfrommer\altaffilmark{1,5},
A. Pinzke\altaffilmark{6}}

\altaffiltext{1}{Corresponding authors: N. Karlsson, nkarlsson@physics.umn.edu \& C. Pfrommer, christoph.pfrommer@h-its.org}
\altaffiltext{2}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
\altaffiltext{3}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
\altaffiltext{4}{Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm, Germany}
\altaffiltext{5}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
\altaffiltext{6}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}

>>>>

%\title{VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
%\title{Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
\title{Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi}
\author{
T. Arlen\altaffilmark{1},
M. Beilicke\altaffilmark{2},
W. Benbow\altaffilmark{3},
V. Bugaev\altaffilmark{2},
K. Byrum\altaffilmark{4},
A. Cannon\altaffilmark{5},
A. Cesarini\altaffilmark{6},
L. Ciupik\altaffilmark{7},
J. Dumm\altaffilmark{8},
G. Finnegan\altaffilmark{9},
L. Fortson\altaffilmark{8},
A. Furniss\altaffilmark{10},
N. Galante\altaffilmark{3},
G. Gyuk\altaffilmark{7},
P. Kaaret\altaffilmark{11},
N. Karlsson\altaffilmark{8,23},
D. Kieda\altaffilmark{9},
H. Krawczynski\altaffilmark{2},
G. Maier\altaffilmark{12},
P. Majumdar\altaffilmark{1},
S. McArthur\altaffilmark{2},
A. McCann\altaffilmark{13},
P. Moriarty\altaffilmark{14},
A. N. Otte\altaffilmark{15},
J. S. Perkins\altaffilmark{16,17},
M. Pohl\altaffilmark{18,12},
H. Prokoph\altaffilmark{12},
E. Roache\altaffilmark{3},
J. Ruppel\altaffilmark{18,12},
D. B. Saxon\altaffilmark{19},
G. H. Sembroski\altaffilmark{20},
C. Skole\altaffilmark{12},
I. Telezhinsky\altaffilmark{18,12},
G. Te\v{s}i\'{c}\altaffilmark{13},
S. Thibadeau\altaffilmark{2},
R. Welsing\altaffilmark{12}}

%%\email{nkarlsson@physics.umn.edu}
\and
\author{S. Federici\altaffilmark{12,18}, C. Pfrommer\altaffilmark{21,23},
A. Pinzke\altaffilmark{22}}

%% affiliations
\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA 90095, USA}
\altaffiltext{2}{Department of Physics, Washington University, St. Louis, MO 63130, USA}
\altaffiltext{3}{Fred Lawrence Whipple Observatory, Harvard-Smithsonian Center for Astrophysics, Amado, AZ 85645, USA}
\altaffiltext{4}{Argonne National Laboratory, 9700 S. Cass Avenue, Argonne, IL 60439, USA}
\altaffiltext{5}{School of Physics, University College Dublin, Belfield, Dublin 4, Ireland}
\altaffiltext{6}{School of Physics, National University of Ireland Galway, University Road, Galway, Ireland}
\altaffiltext{7}{Astronomy Department, Adler Planetarium and Astronomy Museum, Chicago, IL 60605, USA}
\altaffiltext{8}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
\altaffiltext{9}{Department of Physics and Astronomy, University of Utah, Salt Lake City, UT 84112, USA}
\altaffiltext{10}{Santa Cruz Institute for Particle Physics and Department of Physics, University of California, Santa Cruz, CA 95064, USA}
\altaffiltext{11}{Department of Physics and Astronomy, University of Iowa, Van Allen Hall, Iowa City, IA 52242, USA}
\altaffiltext{12}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
\altaffiltext{13}{Physics Department, McGill University, Montreal, QC H3A 2T8, Canada}
\altaffiltext{14}{Department of Life and Physical Sciences, Galway-Mayo Institute of Technology, Dublin Road, Galway, Ireland}
\altaffiltext{15}{School of Physics \& Center for Relativistic Astrophysics, Georgia Institute of Technology, 837 State Street NW, Atlanta, GA 30332-0430}
\altaffiltext{16}{CRESST and Astroparticle Physics Laboratory NASA/GSFC, Greenbelt, MD 20771, USA.}
\altaffiltext{17}{University of Maryland, Baltimore County, 1000 Hilltop Circle, Baltimore, MD 21250, USA.}
\altaffiltext{18}{Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm,Germany}
\altaffiltext{19}{Department of Physics and Astronomy and the Bartol Research Institute, University of Delaware, Newark, DE 19716, USA}
\altaffiltext{20}{Department of Physics, Purdue University, West Lafayette, IN 47907, USA }
\altaffiltext{21}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
\altaffiltext{22}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
\altaffiltext{23}{Corresponding authors: N. Karlsson, nkarlsson@physics.umn.edu \& C. Pfrommer, christoph.pfrommer@h-its.org}
